Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-01 sattose/paper.tex
Yet better graphicz
Bit of layout considerations
Getting there...

\begin{figure}[H]
  \caption{Amount of times a clone with a certain number of tokens has a certain number of nodes.}
    \includegraphics[width=1\columnwidth]{img/TokenThreshold}
  \label{fig:tokenthreshold}
\end{figure}

@@

\begin{figure}[H]
  \caption{Number of cloned declarations/statements.}
    \includegraphics[width=1\columnwidth]{img/TypeResults}
  \label{fig:typeres}
\end{figure}

In this figure the number of cloned statements per clone type are displayed. The difference between T1R and T1 is small (10.9\%), because most often textually equal code is also functionally equal. The difference between T2R and T2 is bigger (34.7\%), mainly because we allow no variability in used types. T3R and T3 are similar to T2R and T2, because our dataset does not have so many gapped clones for the thresholds used.

We also measured the duration of finding clones by the different clone types. Fig.~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types. Although this data is dependent on the implementation, there is a notable difference between the refactoring-oriented clone types and the literature clone types. Most of the time that the refactoring-oriented clone types take longer is spent resolving symbols (to infer FQIs).

\begin{figure}[H]
  \caption{Duration in minutes of identifying clones for clone type definitions.}
    \includegraphics[width=1\columnwidth]{img/DurationChart}
  \label{fig:performance}
\end{figure}

@@

Fig.~\ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances. The relation of clones through inheritance is measured on clone class level: it involves all child clone instances. The location and contents of clones is measured on clone instance level. A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50). A clone instance contents consists of a list of all statements and declarations it spans.

@@

Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other. To do this, they first define several categories for the relation between clone instances in object-oriented languages. These categories are shown in Fig.~\ref{fig:clonerelation}. These categories are as follows:
\begin{enumerate}
  \item \textbf{Same method}: All instances of the clone class are in the same method.
  \item \textbf{Same class}: All instances of the clone class are in the same class.
  \item \textbf{Superclass}: All instances of the clone class are children and parents of each other.
  \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
  \item \textbf{Sibling class}: All instances of the clone class have the same parent class.
  \item \textbf{First cousin class}: All instances of the clone class have the same grandparent class.
\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same hierarchy, but do not belong to any of the other categories.
\item \textbf{Same external superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
\end{enumerate}

>>>>

\begin{figure}[H]
  \caption{Amount of times a clone with a certain number of tokens has a certain number of nodes.}
    \includegraphics[width=.95\columnwidth]{img/TokenThreshold}
  \label{fig:tokenthreshold}
\end{figure}

@@

\begin{figure}[H]
  \caption{Number of cloned declarations/statements.}
    \includegraphics[width=.9\columnwidth]{img/TypeResults}
  \label{fig:typeres}
\end{figure}

In this figure the number of cloned nodes per clone type are displayed. The difference between T1R and T1 is small (10.9\%), because most often textually equal code is also functionally equal. The difference between T2R and T2 is bigger (34.7\%), mainly because we allow no variability in used types. T3R and T3 are similar to T2R and T2, because our dataset does not have so many gapped clones for the thresholds used.

We also measured the duration of finding clones by the different clone types. Fig.~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types. Although this data is partly dependent on our implementation of the clone types, there is a notable difference between the refactoring-oriented clone types and the literature clone types. The reason for this is further explained in section \ref{chap:challenge}.

\begin{figure}[H]
  \caption{Duration in minutes of identifying clones for clone type definitions.}
    \includegraphics[width=.9\columnwidth]{img/DurationChart}
  \label{fig:performance}
\end{figure}

@@

Fig.~\ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances. The relation of clones through inheritance is measured for each clone class. The location and contents of clones are measured for each clone instance.

@@

Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other. To do this, they first define several categories for the relation between clone instances in object-oriented languages. These categories are as follows:
\begin{enumerate}
  \item \textbf{Same method}: All instances of the clone class are in the same method.
  \item \textbf{Same class}: All instances of the clone class are in the same class.
  \item \textbf{Superclass}: All instances of the clone class are children and parents of each other.
  \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
  \item \textbf{Sibling class}: All instances of the clone class have the same parent class.
  \item \textbf{First cousin class}: All instances of the clone class have the same grandparent class.
\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same hierarchy, but do not belong to any of the other categories.
\item \textbf{Same external superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
\end{enumerate}
